\documentclass[10pt,oneside]{amsart}
\setcounter{tocdepth}{1}

%\usepackage{../macros}

%for arxiv 
\usepackage{macros}

%\reversemarginpar

\def\brian{\textcolor{blue}{BW: }\textcolor{blue}}
\def\owen{\textcolor{red}{OG: }\textcolor{red}}
\def\si{\marginpar{\textcolor{blue}{Edits here}}}

\title{Chiral differential operators via\\quantization of the holomorphic $\sigma$-model}

\author{Vassily Gorbounov}
\address{University of Aberdeen,
Higher School of Economics, and the Laboratory of Algebraic Geometry and Homological Algebra at the Moscow Institute of Physics and Technology}
\email{ vgorb10@gmail.com}
%\urladdr{http://people.mpim-bonn.mpg.de/gwilliam/}

\author{Owen Gwilliam}
\address{University of Massachusetts, Amherst}
\email{gwilliam@math.umass.edu}
\urladdr{http://people.math.umass.edu/~gwilliam/}

\author{Brian Williams}
\address{Northeastern University}
\email{brianwilliams.math@gmail.com}
\urladdr{https://web.northeastern.edu/brwilliams/}

\begin{document}
\maketitle

\begin{abstract}
The curved $\beta\gamma$ system is a nonlinear $\sigma$-model with a Riemann surface as the source and a complex manifold $X$ as the target. Its classical solutions pick out the holomorphic maps from the Riemann surface into $X$. Physical arguments identify its algebra of operators with a vertex algebra known as the chiral differential operators (CDO) of $X$. We verify these claims mathematically by constructing and quantizing rigorously this system using machinery developed by Kevin Costello and the second author, which combine renormalization, the Batalin-Vilkovisky formalism, and factorization algebras. Furthermore, we find that the factorization algebra of quantum observables of the curved $\beta\gamma$ system encodes the sheaf of chiral differential operators. In this sense our approach provides deformation quantization for vertex algebras. As in many approaches to deformation quantization, a key role is played by Gelfand-Kazhdan formal geometry. We begin by constructing a quantization of the $\beta\gamma$ system with an $n$-dimensional formal disk as the target. There is an obstruction to quantizing equivariantly with respect to the action of formal vector fields $\Vect$ on the target disk, and it is naturally identified with the first Pontryagin class in Gelfand-Fuks cohomology. Any trivialization of the obstruction cocycle thus yields an equivariant quantization with respect to an extension of $\Vect$ by $\hOmega^2_{cl}$, the closed 2-forms on the disk. By machinery mentioned above, we then naturally obtain a factorization algebra of quantum observables, which has an associated vertex algebra easily identified with the formal $\beta\gamma$ vertex algebra. Next, we introduce a version of Gelfand-Kazhdan formal geometry suitable for factorization algebras, and we verify that for a complex manifold $X$ with trivialized first Pontryagin class, the associated factorization algebra recovers the vertex algebra of CDOs of~$X$.\\

Le syst\`{e}me b\^{e}ta gamma incurv\'{e} est un mod\`{e}le sigma nonlin\'{e}aire de
source une surface de Riemann et de cible une vari\'{e}t\'{e} complexe $X$. Ses
solutions classiques sont donn\'{e}es par des cartes holomorphes de la
surface de Riemann dans $X$. Les arguments physiques identifient son
alg\`{e}bre d'op\'{e}rateurs avec une alg\`{e}bre vertex connue sous le nom
d'op\'{e}rateurs diff\'{e}rentiels chiraux (CDO) de $X$. Nous v\'{e}rifions ces
affirmations de mani\`{e}re math\'{e}matique en construisant et en quantifiant
rigoureusement ce syst\`{e}me en utilisant sur les techniques d\'{e}velopp\'{e}es
par Kevin Costello et le second auteur, combinant \`{a} la fois les outils
de la renormalisation, le formalisme de Batalin-Vilkovisky, et les
alg\`{e}bres \`{a} factorisation. En outre, nous prouvons que l'alg\`{e}bre \`{a}
factorisation des observables quantiques du syst\`{e}me b\^{e}ta gamma courb\'{e}
encode les gerbes d'op\'{e}rateurs diff\'{e}rentiels chiraux. En un sens,
notre approche fournit une quantification par d\'{e}formation pour les
alg\`{e}bres de vertex. Comme dans de nombreuses approches \`{a} la
quantification par d\'{e}formations, la g\'{e}om\'{e}trie formelle de
Gelfand-Kazhdan joue un rôle cl\'{e}. Nous commençons par construire une
quantification du syst\`{e}me b\^{e}ta gamma \`{a} valeur un disque formel de
dimension n. Il existe une obstruction \`{a} l'existence d'une
quantification qui soit \'{e}quivariante par rapport \`{a} l'action des champs
de vecteurs formels sur le disque; cette obstruction s'identifie
naturellement \`{a} la premi\`{e}re classe de Pontryagin de la cohomologie de
Gelfand-Fuks. Toute trivialisation du cocycle d'obstruction donne
ainsi une quantification \'{e}quivariante vis-\`{a}-vis d'une extension de
champs de vecteurs formels par les 2-formes ferm\'{e}es sur le disque.
D'apr\`{e}s les r\'{e}sultats cit\'{e} ci-dessus, nous en d\'{e}duisons
naturellement une alg\`{e}bre \`{a} factorisation d'observables quantiques, \`{a}
laquelle est associ\'{e}e une alg\`{e}bre de vertex qui s'identifie \`{a}
l'alg\`{e}bre vertex formelle de type beta gamma. Par ailleurs, nous
introduisons une version de la g\'{e}om\'{e}trie formelle de Gelfand-Kazhdan
adapt\'{e}e aux alg\`{e}bres \`{a} factorisation et nous v\'{e}rifions que, pour une
vari\'{e}t\'{e} complexe munie d'une trivialisation de sa premi\`{e}re classe de
Pontryagin, l'alg\`{e}bre \`{a} factorisation associ\'{e}e d\'{e}crit l'alg\`{e}bre vertex.
\end{abstract}


%\begin{abstract}
%We show that the local observables of the curved $\beta\gamma$ system
%encode the sheaf of chiral differential operators using the machinery of \cite{CG1, CG2}, 
%which combine renormalization, the Batalin-Vilkovisky formalism, and factorization algebras. 
%Our approach is in the spirit of deformation quantization via Gelfand-Kazhdan formal geometry.
%We begin by constructing a quantization of the $\beta\gamma$ system with an $n$-dimensional formal disk as the target. There is an obstruction to quantizing equivariantly with respect to the action of formal vector fields $\Vect$ on the target disk, and it is naturally identified with the first Pontryagin class in Gelfand-Fuks cohomology.
%Any trivialization of the obstruction cocycle thus yields an equivariant quantization with respect to an extension of $\Vect$ by $\hOmega^2_{cl}$, the closed 2-forms on the disk. By results in \cite{CG1}, we then naturally obtain a factorization algebra of quantum observables, which has an associated vertex algebra easily identified with the formal $\beta\gamma$ vertex algebra. Next, we introduce a version of Gelfand-Kazhdan formal geometry suitable for factorization algebras, and we verify that for a complex manifold $X$ with trivialized first Pontryagin class, the associated factorization algebra recovers the vertex algebra of CDOs of~$X$.\\
%\end{abstract}

\input{intro}
\tableofcontents
\input{part1}
\input{part2}
\input{part3}
\input{appx}

\addtocontents{toc}{\protect\setcounter{tocdepth}{0}}
\addcontentsline{toc}{section}{References}
\bibliographystyle{amsalpha}
\bibliography{refs}

\end{document}